### 2020-12-18 Thesis-Chapter6-ThreatModel.tex
Editorial improvements

The amount of risk \ldawmsr introduces depends on the number of suggested mitigations that are implemented. Some threats
introduce inherently little risk due to their difficult nature and low pay off. Others introduce greater risk but can be
reasonably mitigated. Some threats specifically target transparency, and therefore are difficult to address without
trust. Finally, there are some risks that cannot be safely mitigated. Each of these classes of threats are discussed in
turn.

\ii{S6}, \ii{T1}, \ii{T3}, \ii{I1}, \ii{I3}, \ii{I6}, \ii{D1}, \ii{D2}, and \ii{E1} \ii{E2} are each low-risk. They
either fail to produce useful results, can be reasonably mitigated, or are a threat that is already present in the
baseline depicted in \mysec{sec-basic-dar}. Although these threats are not fatal flaws to a design, it is important for
a designer to consider and mitigate the risk they pose. Unless they appear in combination with other threats, they do
not deserve more discussion.

@@

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal processes and cooperation of several parties. Even in the U.S., the legal process may involve secret courts,
secret investigations, and secrecy orders on the vendor \cite{shamsi_2011}. Under these conditions, transparency is
difficult to achieve. A destructive disassembly requirement provides non-repudiation that the device was unlocked, if
and only if one has physical access to the device. Technically enforced transparency into device access requests and
responses would grant non-repudiation at a broader level. \ldawmsr does not include a mechanism for the feature, though
other \ac{DAR} \ac{EA} proposals do \cite{phan_key_2017} \cite{servan_schreiber_jje_2020} \cite{goldwasser_public_2017}.
Unfortunately, building this feature into a proposal makes it potentially vulnerable the hawkish lawmaker, who may
consider too much transparency to be an anti-feature.

Finally, there are the threats of \ii{I4}, \ii{I5}, and \ii{E3}, which each represent the disclosure of unlock artifact
data (the DID-DSK database). These threats create a large amount of risk that cannot be safely mitigated. Storing so
much sensitive data in a central database creates a high-value target for foreign intelligence and cyber criminals. The
vendor needs to protect this database from the most advanced attackers in the world while regularly updating and
accessing it. \Acp{HSM} and robust security policies would make that a difficult task. The data will almost certainly
leak eventually. The effects of such an event would depend on who stole the unlock artifacts. Criminals would use the
data for personal and financial gain; foreign intelligence and authoritarian regimes would use it to spy on their
enemies. In the worst-case scenario, anyone with specialized tools and disregard for the law could get into any
compliant device after disassembling it and waiting through the time vault.

@@

\paragraph*{Security} Security has already been discussed at length in this chapter. \ldawmsr introduces significant
risk in the DID-DSK database itself, but performs well in many other respects, especially if the recommended mitigations
are implemented. It goes from very hard to attack, when everything is working as intended, to simple to attack, when the
database is leaked. However, even when it becomes trivial to attack, the attackers are limited to devices in their
physical possession and cannot hide access from their victims.

\paragraph*{Protection of civil liberties} This goal was defined as defending against \ac{masssurv} and abuse by
authoritarian regimes. \ldawmsr does an excellent job of protecting against \ac{masssurv} due to its physicality. Any
power cannot abuse this technology at scale. It is not as strong at protecting against authoritarian regimes. Prior to a
leak, vendors would face intense and possibly coercive legal pressure to unlock devices in foreign countries. After a
leak, these regimes could get into any device they want. If one lived in a country that was willing to take and destroy
their devices to read their contents without legal due process, this would be an unwelcome technology.

\paragraph*{Transparency} \ldawmsr provides transparency to the device user, but does not provide transparency to the
public. Due to destructive disassembly (or the hardware transparency mechanism), whether a device has been accessed
using this method is irrefutable. However, this can only be confirmed if the device is available. Neither the user nor
the public can detect if a device has been unlocked under secretive conditions, whether lawfully or criminally. This
leaves allows the potential for government abuse---though again with the caveat that physical possession requirements
mean it cannot be abused without a trace.

\paragraph*{Law enforcement utility} \ldawmsr includes a few tradeoffs between security and law enforcement utility. The
requirements to have physical possession of the device, to wait through the time vault, and to limit the number of
authorized law enforcement laboratories all create barriers to usability. The physical possession requirement is far too
important for security and civil liberties to sacrifice for utility. Furthermore, law enforcement, and search and
seizure law generally, is geared towards physical evidence already. The time vault prevents against time-sensitive
threats, though destructive disassembly (not part of the original proposal) may be enough to cover these cases as well,
so the time vault could be decreased without significant impact. Limiting the number of laboratories able to use the
system reduces the risk of spoofing attacks; local law enforcement would have to cooperate with one of these special
laboratories, such as a regional \ac{FBI} office. (This really just shifts the spoofing threat up a level, though the
shift is appropriate.) In the end, law enforcement still has a reliable way to get into lawfully seized devices.
\ldawmsr upholds its end, but the government must fund the \ac{FBI} operation and cultivate cooperation between local
and federal agencies.

>>>>

The amount of risk \ldawmsr introduces depends on the number of suggested mitigations that are implemented. Some
possible attacks introduce inherently little risk due to their difficult nature and low pay off. Others introduce
greater risk but can be reasonably addressed. Some threats specifically target transparency, and therefore are difficult
to address without trust. Finally, there are some risks that cannot be safely mitigated. Each of these classes of
threats are discussed in turn.

\ii{S6}, \ii{T1}, \ii{T3}, \ii{I1}, \ii{I3}, \ii{I6}, \ii{D1}, \ii{D2}, and \ii{E1} \ii{E2} are each low-risk. They
either are preventable, unuseful, or already present in the baseline depicted in \mysec{sec-basic-dar}. Although these
threats are not fatal flaws to a design, it is important for a designer to consider and mitigate the risk they pose.
Unless they appear in combination with other threats, they do not deserve more discussion.

@@

\ii{R2}, \ii{R3}, and \ii{R4} are repudiation attacks that belie the system's potential for abuse. The system relies on
legal processes and cooperation of several parties. Even in the U.S., the legal process may involve secret courts,
secret investigations, and secrecy orders on the vendor \cite{shamsi_2011}. Under these conditions, transparency is
difficult to achieve. The destructive disassembly requirement enables transparency at a device level. Auditable logs of
device access \ii{requests and responses} would enable transparency at a system level. \ldawmsr does not create such a
log, though other \ac{DAR} \ac{EA} proposals do \cite{phan_key_2017} \cite{servan_schreiber_jje_2020}
\cite{goldwasser_public_2017}. Unfortunately, building this feature into a proposal makes it potentially vulnerable the
hawkish lawmaker, who may consider too much transparency to be an anti-feature.

Finally, there are the threats of \ii{I4}, \ii{I5}, and \ii{E3}, which each represent the disclosure of unlock artifact
data (the DID-DSK database). These threats create a large amount of risk that cannot be safely mitigated. Storing so
much sensitive data in a central database creates a high-value target for foreign intelligence and cyber criminals. The
vendor needs to protect this database from the most advanced attackers in the world while also regularly updating and
accessing it. \Acp{HSM} and robust security policies would make that a difficult task. The data will almost certainly
leak eventually. The effects of such an event would depend on who stole the unlock artifacts. Criminals would use the
data for personal and financial gain; foreign intelligence and authoritarian regimes would use it to spy on their
enemies. In the worst-case scenario, anyone with specialized tools and disregard for the law could get into any
compliant device after disassembling it and waiting through the time vault.

@@

\paragraph*{Security} Security has already been discussed at length in this chapter. \ldawmsr introduces significant
risk in the DID-DSK database itself, but performs well in many other respects, especially if the recommended mitigations
are implemented. When the unlock artifacts are disclosed, the system becomes simple to attack. However, even in these
conditions, attackers are limited to devices in their physical possession and cannot hide access from their victims.

\paragraph*{Protection of civil liberties} This goal was defined as defending against \ac{masssurv} and abuse by
authoritarian regimes. \ldawmsr successfully protects against \ac{masssurv} due to the physical possession and
destructive disassembly requirements. It is not as effective against authoritarian regimes, which would put intense and
possibly coercive legal pressure on vendors to unlock devices. In the case of an unlock artifacts leak, regimes could
broadly abuse the system. This technology would be unwelcome to those living in countries that do not respect rule of
law.

\paragraph*{Transparency} \ldawmsr provides transparency to the device user, but does not provide transparency to the
public. As discussed in the previous section, the destructive disassembly requirement would result in transparency at
the device level. However, access to a device can only be confirmed if the device is available. Neither the user nor the
public can detect if a device has been unlocked under secretive conditions, whether lawfully or criminally. This creates
potential for government abuse.

\paragraph*{Law enforcement utility} \ldawmsr includes a few tradeoffs between security and law enforcement utility. The
requirements to have physical possession of the device, to wait through the time vault, and to limit the number of
authorized law enforcement laboratories all create barriers to usability. The physical possession requirement is too
important for security to be compromised for utility. Additionally, search and seizure law is already designed for
physical evidence; maintaining the possession requirement makes the system operate within well-understood norms. The
time vault prevents against time-sensitive attacks, though destructive disassembly (not part of the original proposal)
may be enough to cover these cases. The time vault period could be decreased without significant impact. Limiting the
number of laboratories that can use the system reduces the risk of spoofing attacks; local law enforcement would have to
cooperate with one of these special laboratories, such as a regional \ac{FBI} office, to unlock a device. In the end,
law enforcement still has a reliable way to get into lawfully seized devices. \ldawmsr upholds its end, but the
government must fund the \ac{FBI} operation and cultivate cooperation between local and federal agencies.
